cardinalR: Generating interesting high-dimensional data structures

### 2025-06-24 paper-cardinalR.Rmd
Updated acknowledgment only with source code

The package is available at [https://github.com/JayaniLakshika/cardinalR](https://github.com/JayaniLakshika/cardinalR), and source material for this paper is available at [https://github.com/JayaniLakshika/paper-cardinalR](https://github.com/JayaniLakshika/paper-cardinalR).

>>>>

The source material for this paper is available at [https://github.com/JayaniLakshika/paper-cardinalR](https://github.com/JayaniLakshika/paper-cardinalR).
